---
title: "Data preparation"
output:
  pdf_document: default
---

# Instructions

- You only need to submit the .Rmd of this file, not a PDF.

- You should __comment__ your code clearly to show what you've done to prepare the data.

- The purpose of this file is to use the data in the `data-raw` folder to create the data you will use in the report. The data you will use in the report should be saved in the `data` folder. It is good professional practice to make sure you're never directly modifying your raw data, but instead creating new datasets based on merges/manipulations that you need to reuse.

- Make sure you've taken a look at the hints for the web scraping and census API. 

- You may find the `write_rds()` function from the `readr` package helpful (it is loaded as part of the `tidyverse`).

- You do not need to keep the structure below.

# Set up

```{r, libraries}
# Set up any libraries you need
library(dplyr)
library(tidyverse)
library(ggplot2)
```

# Loading client data

```{r}
# load the data
break_glass_in_case_of_emergency <- readRDS("~/sta303-w22-final-project-template/data-raw/break_glass_in_case_of_emergency.Rds")

cust_dev <- readRDS("~/sta303-w22-final-project-template/data-raw/cust_dev.Rds")

cust_sleep <- readRDS("~/sta303-w22-final-project-template/data-raw/cust_sleep.Rds")

customer <- readRDS("~/sta303-w22-final-project-template/data-raw/customer.Rds")

device <- readRDS("~/sta303-w22-final-project-template/data-raw/device.Rds")

f <- file.choose()
break_glass_in_case_of_emergency <- readRDS(f)
f <- file.choose()
cust_dev <- readRDS(f)
f <- file.choose()
cust_sleep <- readRDS(f)
f <- file.choose()
customer <- readRDS(f)
f <- file.choose()
device <- readRDS(f)

```

# Getting external data

## Web scraping industry data

```{r}
# These are the libraries I find useful for webscraping
library(tidyverse)
library(polite)
library(rvest)

url <- "https://fitnesstrackerinfohub.netlify.app/"

# Make sure this code is updated appropriately to provide 
# informative user_agent details
target <- bow(url,
              user_agent = "liza.bolton@utoronto.ca for STA303/1002 project",
              force = TRUE)

# Any details provided in the robots text on crawl delays and 
# which agents are allowed to scrape
target

html <- scrape(target)

device_data <- html %>% 
  html_elements("table") %>% 
  html_table() %>% 
  pluck(1) # added, in case you're getting a list format

```

# Census API

```{r}
# install.packages("cancensus")
library(cancensus)


options(cancensus.api_key = "CensusMapper_cf78c5571bf66af9d889cac93d9ef013",
        cancensus.cache_path = "cache") # this sets a folder for your cache


# get all regions as at the 2016 Census (2020 not up yet)
regions <- list_census_regions(dataset = "CA16")

regions_filtered <-  regions %>% 
  filter(level == "CSD") %>% # Figure out what CSD means in Census data
  as_census_region_list()

# This can take a while
# We want to get household median income
census_data_csd <- get_census(dataset='CA16', regions = regions_filtered,
                          vectors=c("v_CA16_2397"), 
                          level='CSD', geo_format = "sf")

# Simplify to only needed variables
median_income <- census_data_csd %>% 
  as_tibble() %>% 
  select(CSDuid = GeoUID, contains("median"), Population) %>% 
  mutate(CSDuid = parse_number(CSDuid)) %>% 
  rename(hhld_median_inc = 2)
```
```{r}
library(haven)
library(tidyverse)
f <- file.choose()
dataset = read_sav(f)

postcode <- dataset %>% 
  select(PC, CSDuid)
```


```{r, warning=FALSE}
library(eeptools)
# dataset containing all customers
data <- full_join(cust_dev, customer, by = "cust_id") %>%
  left_join(device, by = "dev_id")

# join postal code dataset with median income
postal_income <- full_join(break_glass_in_case_of_emergency, median_income, by = "CSDuid") %>%
  rename(postcode = PC)

# match median income with each customer by postal code
data <- left_join(data,postal_income, by = "postcode")

# calculate age
data <- data %>%  
  mutate(age = age_calc(dob,units = "years")) %>%
  mutate(age_group = if (age > 70) {
    age_group = "over 70"
  } else if (age > 60) {
    age_group = "60~70"
  } else if (age > 50) {
    age_group = "50~60"
  } else if (age > 40) {
    age_group = "40~50"
  } else if (age > 30) {
    age_group = "30~40"
  } else if (age > 20) {
    age_group = "20~30"
  } else 
    age_group = "under 20")


# dataset containing only customers using active product
old_data <- data %>%
  filter(line == "Run"|line == "IDOL")

# dataset containing both advance and active
new_data <- data %>%
  filter(line == "Active"|line == "Advance")
```
```{r}
# EDA

# age
hist(data$age, breaks = 20)
hist(new_data$age, breaks = 20)
hist(old_data$age, breaks = 20)
# an age gap in active data
```
```{r}
# sex
ggplot(data, aes(x = sex)) + geom_bar()
ggplot(new_data, aes(x = sex)) + geom_bar()
ggplot(old_data, aes(x = sex)) + geom_bar()
sex_proportion <- data %>%
  group_by(sex) %>%
  summarise(prop = n()/29372)
sex_proportion <- new_data %>%
  group_by(sex) %>%
  summarise(prop = n()/15629)
sex_proportion <- old_data %>%
  group_by(sex) %>%
  summarise(prop = n()/13471)

data = data %>% mutate(new_customer = ifelse(line == "Active" | line == "Advance", 1,0))
```
```{r}
# emoji
ggplot(data, aes(x = emoji_modifier, fill = sex)) + geom_bar()
ggplot(new_data, aes(x = emoji_modifier, fill = sex)) + geom_bar()
ggplot(old_data, aes(x = emoji_modifier, fill = sex)) + geom_bar()
```
```{r}
ggplot(data, aes(x = emoji_modifier, fill = age_group)) + geom_bar()
ggplot(new_data, aes(x = emoji_modifier, fill = age_group)) + geom_bar()
ggplot(old_data, aes(x = emoji_modifier, fill = age_group)) + geom_bar()
```
```{r}
# device name
ggplot(data, aes(x = device_name, fill = sex)) + geom_bar() + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
ggplot(new_data, aes(x = device_name, fill = sex)) + geom_bar() + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
ggplot(old_data, aes(x = device_name, fill = sex)) + geom_bar() + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
```
```{r}
ggplot(data, aes(x = device_name, fill = age_group)) + geom_bar() + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
ggplot(new_data, aes(x = device_name, fill = age_group)) + geom_bar() + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
ggplot(old_data, aes(x = device_name, fill = age_group)) + geom_bar() + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
```
```{r}
ggplot(data, aes(x = age, y = hhld_median_inc, color = line)) + geom_smooth()
ggplot(new_data, aes(x = age, y = hhld_median_inc, color = emoji_modifier)) + geom_smooth()
ggplot(old_data, aes(x = age, y = hhld_median_inc, color = emoji_modifier)) + geom_smooth()
```
```{r}
hist(data$hhld_median_inc, breaks = 100, xlim = c(40000,200000))
hist(new_data$hhld_median_inc, breaks = 100, xlim = c(40000,120000))
hist(old_data$hhld_median_inc, breaks = 50, xlim = c(40000,120000))

```

```{r}
ggplot(data, aes(x = hhld_median_inc, color = sex, )) + geom_bar()  +
    scale_x_continuous(breaks = 1:50) + facet_wrap(~emoji_modifier)


  
data$Population <- as.numeric(data$Population)
```

```{r}
m1 <- lm(hhld_median_inc ~ new_customer, data = data)
summary(m1)
confint(m1)

model <- glm(new_customer ~ hhld_median_inc + age + sex + emoji_modifier, family= binomial(link = "logit"), data = data)
summary(model)

model2 <- glm(new_customer ~ hhld_median_inc + age + sex + emoji_modifier, family= binomial(link = "logit"), data = data)
summary(model2)
```

```{r}
sleep_data <- left_join(cust_sleep, data, by = "cust_id") %>%
  na.omit(emoji_modifier)

sleep_data$age <- round(sleep_data$age, 0)

sleep_data <- sleep_data %>% 
  mutate(colour = case_when(emoji_modifier == "U+1F3FB" ~ "Light",
                            emoji_modifier == "U+1F3FC" ~ "Medium light",
                            emoji_modifier == "U+1F3FD" ~ "Medium",
                            emoji_modifier == "U+1F3FE" ~ "Medium Dark",
                            emoji_modifier == "U+1F3FF" ~ "Dark"))

sleep_data <- sleep_data %>%
  mutate(flag_permin = flags/duration)

unique_sleep_data <- sleep_data %>%
  group_by(cust_id) %>%
  summarise(avg = mean(flag_permin)) %>%
  left_join(customer, by = "cust_id")

hist(sleep_data$duration)
hist(sleep_data$flags)

hist(unique_sleep_data$avg, breaks = 20)
hist(sleep_data$flag_permin, breaks = 20)
hist(sleep_data$flags, breaks = 50)
hist(sleep_data$duration/sleep_data$flags, breaks = 20)

model_s <- glm(flags ~ colour, family = "poisson", data = sleep_data)
summary(model_s)

library(lme4)
model_s <- glmer(flags ~ colour + (1|duration), family = "poisson", data = sleep_data)
summary(model_s)

model_ss <- glmer(flags ~ colour + (1|duration) + (1|age), family = "poisson", data = sleep_data)
summary(model_s) 

model_ss <- glmer(flags ~ colour + (1|duration) + (1|age) + (1|sex), family = "poisson", data = sleep_data)
summary(model_sss)

model_sss <- glmer(flags ~ colour + (1|age) + (1|sex) + (1|duration) + (1|age:sex), family = "poisson", data = sleep_data)
summary(model_sss)

model_n <- glmer(flags ~ colour + (1|duration) + (1|age:sex) + (1|Population), family = "poisson", data = sleep_data)

model_nn <- glmer(flags ~ colour + (1|age) + (1|duration) + (1|sex) + (1|age:duration) + (1|age:sex) + (1|Population), family = "poisson", control=glmerControl(optimizer="bobyqa",  optCtrl=list(maxfun=2e5)), data = sleep_data)
summary(model_nn)

lmtest::lrtest(model_sss, model_nn)

vignette("lmer")


m3 = glme
library(tidyverse)
sleep_data %>% 
  ggplot(aes(x = sex, y = flags, colour = colour)) +
  geom_boxplot() +
  facet_wrap(~colour)
mean(sleep_data$flags)
var(sleep_data$flags)
```
```{r}
model_s <- glmer(flags ~ colour + (1|duration), family = "poisson", data = sleep_data)
summary(model_s)

model_ss <- glmer(flags ~ colour + (1|duration) + (1|age_group), family = "poisson", data = sleep_data)
summary(model_s) 

lmtest::lrtest(model_s, model_ss)
```
```{r}
test_data <- na.omit(sleep_data)

model_nn <- glmer.nb(flags ~ colour + (1|age) + (1|duration) + (1|sex) + (1|age:duration) + (1|age:sex) + (1|Population), control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)),data = sleep_data)
summary(model_nn)
```




